Appendix

### 2020-04-20 appendix/appendixV5.Rmd
Further testing

\newpage
\blandscape
```{r, echo=FALSE, fig.width=10, fig.height=10, warning = F,message = FALSE,fig.cap="test size"}

@@

\elandscape

@@

\newpage
### Summary of results
```{r, echo=FALSE, fig.width=20, fig.height=35, fig.cap="test size"}

grid.arrange(f8, f9, f10, 
             f11,f12, f13,
             f14,
             ncol = 2,
             nrow = 4)
#library(ggplot2)

>>>>

\newpage
```{r, echo=FALSE, fig.width=16, fig.height=16, warning = F,message = FALSE}

ggpubr::ggarrange(f1,f2, f3,
                  f4, f5, f6,
                  f7,
#          labels = c("A", "B"),
          ncol = 2, nrow = 4)

\newpage
```{r, echo=FALSE, fig.width=10, fig.height=10, warning = F,message = FALSE,fig.cap="test size"}

@@

@@

\newpage
### Summary of results
```{r, echo=FALSE, fig.width=17, fig.height=24}

grid.arrange(f8, f9, f11, 
             f10,f12, f13,
             f14,
             ncol = 2,
             nrow = 4)
#library(ggplot2)
